### 2013-06-01 inst/examples/BUGS/process-noise-only.Rmd
using better initial conditions

```{r jags-setup}
y <- x 
N <- length(x);
jags.data <- list("N","y")
n.chains <- 6
n.iter <- 1e6
n.burnin <- floor(10000)
n.thin <- max(1, floor(n.chains * (n.iter - n.burnin)/1000))
n.update <- 10
```

@@

```{r allen-model}
K_prior_p <- c(0.01, 40.0)
logr0_prior_p <- c(-6.0, 6.0)
logtheta_prior_p <- c(-6.0, 6.0)

@@

```{r allen-priors, dependson="common-priors"}
K_prior     <- function(x) dunif(x, K_prior_p[1], K_prior_p[2])
logr0_prior <- function(x) dunif(x, logr0_prior_p[1], logr0_prior_p[2])
logtheta_prior <- function(x) dunif(x, logtheta_prior_p[1], logtheta_prior_p[2])
par_priors  <- list(K = K_prior, deviance = function(x) 0 * x, 
                    logr0 = logr0_prior, logtheta = logtheta_prior,
                    stdQ = stdQ_prior)
```

@@

```{r allen-mcmc, dependson=c("allen-model", "allen-pars", "jags-setup"), results="hide"}
jags.params=c("K","logr0","logtheta","stdQ") # be sensible about the order here
jags.inits <- function(){
  list("K"= 10 * rlnorm(1,0, 0.1),
       "logr0"=log( 1 * rlnorm(1,0, 0.5) ),
       "logtheta"=log(  5 * rlnorm(1,0, 0.1) ), 
       "stdQ"= abs( 0.2 * rlnorm(1,0, 0.1)),
       .RNG.name="base::Wichmann-Hill", .RNG.seed=123)
}

@@

# Run again iteratively if we haven't met the Gelman-Rubin convergence criterion
recompile(allen_jags) # required for parallel
allen_jags <- do.call(autojags, list(object=allen_jags, n.update=10, 
                                     n.iter=n.iter, n.thin = n.thin))
```

@@

```{r allen-traces, dependson="allen-mcmc"}
```

```{r allen-posteriors, dependson=c("allen-traces", "allen-priors")}
```

@@

```{r ricker-model}
K_prior_p <- c(0.01, 40.0)
logr0_prior_p <- c(-6.0, 6.0)

@@

```{r ricker-priors, dependson="common-priors"}
K_prior     <- function(x) dunif(x, K_prior_p[1], K_prior_p[2])
logr0_prior <- function(x) dunif(x, logr0_prior_p[1], logr0_prior_p[2])
par_priors <- list(K = K_prior, deviance = function(x) 0 * x, 
                   logr0 = logr0_prior, stdQ = stdQ_prior)
```

@@

```{r ricker-mcmc, dependson="ricker-model"}
# Uniform priors on standard deviation terms
jags.params=c("K","logr0", "stdQ")
jags.inits <- function(){
  list("K"=10 * rlnorm(1,0,.5),
       "logr0"=log(1) * rlnorm(1,0,.5),
       "stdQ"=sqrt(0.05) * rlnorm(1,0,.5),
       .RNG.name="base::Wichmann-Hill", .RNG.seed=123)
}
set.seed(12345) 
ricker_jags <- do.call(jags.parallel, 
                       list(data=jags.data, inits=jags.inits, 
                            jags.params, n.chains=n.chains, 
                            n.iter=n.iter, n.thin=n.thin, n.burnin=n.burnin,
                            model.file="ricker_process.bugs"))
recompile(ricker_jags)
ricker_jags <- do.call(autojags, 
                       list(object=ricker_jags, n.update=10, n.iter=n.iter, 
                            n.thin = n.thin, progress.bar="none"))
```

@@

```{r ricker_traces, dependson="ricker-mcmc"}
```

```{r ricker_posteriors, dependson=c("ricker-traces", "ricker-priors")}
```

@@

```{r myers-model}
logr0_prior_p <- c(-6.0, 6.0)
logtheta_prior_p <- c(-6.0, 6.0)
logK_prior_p <- c(-6.0, 6.0)

@@

```{r myers-priors}
logK_prior     <- function(x) dunif(x, logK_prior_p[1], logK_prior_p[2])
logr_prior     <- function(x) dunif(x, logr0_prior_p[1], logr0_prior_p[2])
logtheta_prior <- function(x) dunif(x, logtheta_prior_p[1], logtheta_prior_p[2])
par_priors <- list( deviance = function(x) 0 * x, logK = logK_prior,
                    logr0 = logr_prior, logtheta = logtheta_prior, 
                    stdQ = stdQ_prior)

@@

```{r myers-mcmc, dependson="myers-model"}
jags.params=c("logr0", "logtheta", "logK", "stdQ")
jags.inits <- function(){
  list("logr0"=log(rlnorm(1,0,.1)), 
       "logK"=log(10 * rlnorm(1,0,.1)),
       "logtheta" = log(2 * rlnorm(1,0,.1)),  
       "stdQ"=sqrt(0.5) * rlnorm(1,0,.1),
       .RNG.name="base::Wichmann-Hill", .RNG.seed=123)
}
set.seed(12345)
myers_jags <- do.call(jags, 
                      list(data=jags.data, inits=jags.inits, jags.params, 
                           n.chains=n.chains, n.iter=n.iter, n.thin=n.thin,
                           n.burnin=n.burnin, model.file="myers_process.bugs"))
recompile(myers_jags)
myers_jags <- do.call(autojags, 
                      list(myers_jags, n.update=10, n.iter=n.iter, 
                           n.thin = n.thin, progress.bar="none"))
```

@@

```{r myers-traces, dependson="myers-mcmc"}
```

@@

```{r deviances, dependson=("posterior-mode","myers-output", "ricker-output", "allen-output", "gp-output", "mle-output") }
```

>>>>

```{r jags-setup-local}
y <- x 
N <- length(x);
jags.data <- list("N","y")
n.chains <- 6
n.iter <- 1e6
n.burnin <- floor(10000)
n.thin <- max(1, floor(n.chains * (n.iter - n.burnin)/1000))
n.update <- 10
```

@@

```{r allen-model-local}
K_prior_p <- c(0.01, 40.0)
logr0_prior_p <- c(-6.0, 6.0)
logtheta_prior_p <- c(-6.0, 6.0)

@@

```{r allen-priors-local, dependson="common-priors"}
K_prior     <- function(x) dunif(x, K_prior_p[1], K_prior_p[2])
logr0_prior <- function(x) dunif(x, logr0_prior_p[1], logr0_prior_p[2])
logtheta_prior <- function(x) dunif(x, logtheta_prior_p[1], logtheta_prior_p[2])
par_priors  <- list(K = K_prior, deviance = function(x) 0 * x, 
                    logr0 = logr0_prior, logtheta = logtheta_prior,
                    stdQ = stdQ_prior)
```

@@

```{r allen-mcmc-local, dependson=c("allen-model-local", "allen-pars", "jags-setup"), results="hide"}
jags.params=c("K","logr0","logtheta","stdQ") # be sensible about the order here
jags.inits <- function(){
  list("K"= 8 * rlnorm(1,0, 0.1),
       "logr0"=log(2 * rlnorm(1,0, 0.5) ),
       "logtheta"=log(  5 * rlnorm(1,0, 0.1) ), 
       "stdQ"= abs( 0.2 * rlnorm(1,0, 0.1)),
       .RNG.name="base::Wichmann-Hill", .RNG.seed=123)
}

@@

# Run again iteratively if we haven't met the Gelman-Rubin convergence criterion
recompile(allen_jags) # required for parallel
allen_jags <- do.call(autojags, list(object=allen_jags, n.update=n.update, 
                                     n.iter=n.iter, n.thin = n.thin))
```

@@

```{r allen-traces, dependson="allen-mcmc-local"}
```

```{r allen-posteriors, dependson=c("allen-traces", "allen-priors-local")}
```

@@

```{r ricker-model-local}
K_prior_p <- c(0.01, 40.0)
logr0_prior_p <- c(-6.0, 6.0)

@@

```{r ricker-priors-local, dependson="common-priors"}
K_prior     <- function(x) dunif(x, K_prior_p[1], K_prior_p[2])
logr0_prior <- function(x) dunif(x, logr0_prior_p[1], logr0_prior_p[2])
par_priors <- list(K = K_prior, deviance = function(x) 0 * x, 
                   logr0 = logr0_prior, stdQ = stdQ_prior)
```

@@

```{r ricker-mcmc-local, dependson="ricker-model-local"}
# Uniform priors on standard deviation terms
jags.params=c("K","logr0", "stdQ")
jags.inits <- function(){
  list("K"=10 * rlnorm(1,0,.5),
       "logr0"=log(1) * rlnorm(1,0,.5),
       "stdQ"=sqrt(0.05) * rlnorm(1,0,.5),
       .RNG.name="base::Wichmann-Hill", .RNG.seed=123)
}
set.seed(12345) 
ricker_jags <- do.call(jags.parallel, 
                       list(data=jags.data, inits=jags.inits, 
                            jags.params, n.chains=n.chains, 
                            n.iter=n.iter, n.thin=n.thin, n.burnin=n.burnin,
                            model.file="ricker_process.bugs"))
recompile(ricker_jags)
ricker_jags <- do.call(autojags, 
                       list(object=ricker_jags, n.update=n.update, n.iter=n.iter, 
                            n.thin = n.thin, progress.bar="none"))
```

@@

```{r ricker-traces, dependson="ricker-mcmc-local"}
```

```{r ricker-posteriors, dependson=c("ricker-traces", "ricker-priors-local")}
```

@@

```{r myers-model-local}
logr0_prior_p <- c(-6.0, 6.0)
logtheta_prior_p <- c(-6.0, 6.0)
logK_prior_p <- c(-6.0, 6.0)

@@

```{r myers-priors-local}
logK_prior     <- function(x) dunif(x, logK_prior_p[1], logK_prior_p[2])
logr_prior     <- function(x) dunif(x, logr0_prior_p[1], logr0_prior_p[2])
logtheta_prior <- function(x) dunif(x, logtheta_prior_p[1], logtheta_prior_p[2])
par_priors <- list( deviance = function(x) 0 * x, logK = logK_prior,
                    logr0 = logr_prior, logtheta = logtheta_prior, 
                    stdQ = stdQ_prior)

@@

```{r myers-mcmc-local, dependson="myers-model-local"}
jags.params=c("logr0", "logtheta", "logK", "stdQ")
jags.inits <- function(){
  list("logr0"=log(rlnorm(1,0,.1)), 
       "logK"=log(10 * rlnorm(1,0,.1)),
       "logtheta" = log(2 * rlnorm(1,0,.1)),  
       "stdQ"=sqrt(0.5) * rlnorm(1,0,.1),
       .RNG.name="base::Wichmann-Hill", .RNG.seed=123)
}
set.seed(12345)
myers_jags <- do.call(jags, 
                      list(data=jags.data, inits=jags.inits, jags.params, 
                           n.chains=n.chains, n.iter=n.iter, n.thin=n.thin,
                           n.burnin=n.burnin, model.file="myers_process.bugs"))
recompile(myers_jags)
myers_jags <- do.call(autojags, 
                      list(myers_jags, n.update=n.update, n.iter=n.iter, 
                           n.thin = n.thin, progress.bar="none"))
```

@@

```{r myers-traces, dependson="myers-mcmc-local"}
```

@@

```{r deviances, dependson=c("posterior-mode", "myers-output", "ricker-output", "allen-output", "gp-output", "mle-output") }
```
